\frenchspacing

\section{Examples}

The examples below are shown in three parts.
The first shows the expected citation and CSL-generated parenthetical citation, prefixed by the source of the example:
\begin{description}
\item[RX]
  Reference examples (A-Z).
  \href{https://library.bath.ac.uk/referencing/harvard-bath}{\emph{Referencing guide: Harvard Bath}}
\item[RL]
  Organise a reference list.
  \href{https://library.bath.ac.uk/referencing/harvard-bath}{\emph{Referencing guide: Harvard Bath}}
\item[RI]
  \href{https://library.bath.ac.uk/images/referencing}{\emph{Referencing images}}
\end{description}
The second shows the reference example itself verbatim.
The third shows the reference as formatted using CSL.

These parts are colour-coded according to whether the generated elements match expectations.
A thick double border is shown underneath mismatched citations,
while mismatched references are separated by a thin double border.

\subsection{Books and book chapters}

\subsubsection*{Book with author(s)}

RX: (Rang et al., 2012) = \cite{rang.etal2012rdp}

Rang, H.P., Dale, M.M., Ritter, J.M., Flower, R.J. and Henderson, G., 2012. \emph{Rang and Dale's pharmacology}. 7th ed. Edinburgh: Elsevier Churchill Livingstone.


RX: (Open University, 1972) = \cite{ou1972em}

Open University, 1972. \emph{Electricity and magnetism}. Bletchley: Open University Press.


RX: (Solomon et al., 2019) = \cite{solomon.etal2019cbe}

Solomon, M.R., Askegaard, S., Hogg, M. and Bamossy, G.J., 2019. \emph{Consumer behaviour: a European perspective}. 7th ed. Harlow: Pearson.



\subsubsection*{Book with editor(s) instead of author(s)}

RX: (Rothman, Greenland and Lash, 2008) = \cite{rothman.etal2008me}

Rothman, K.J., Greenland, S. and Lash, T.L., eds, 2008. \emph{Modern epidemiology}. 3rd ed. Philadelphia, Pa.: Lippincott Williams \& Wilkins.



\subsubsection*{Electronic book}

RX: (Haynes, 2014) = \cite{haynes2014crc}

Haynes, W.M., ed., 2014. \emph{CRC handbook of chemistry and physics} [Online]. 94th ed. Boca Raton, Fla.: CRC Press/Taylor and Francis. Available from: \url{http://www.hbcpnetbase.com} [Accessed 16 June 2016].


RX: (Blockley, 2021) = \cite{blockley2021evs}

Blockley, D., 2021. \emph{Engineering: a very short introduction} [Online]. Oxford: Oxford University Press. Available from: \url{https://www.amazon.co.uk/kindle} [Accessed 30 June 2021].



\subsubsection*{Book known by its title}

RX: (British National Formulary, 2020) = \cite{bnf2020}

British National Formulary, 2020. 79th ed. London: Pharmaceutical Press.


The following entries are not in the specification, but test the robustness of the CSL style.

(British National Formulary, 2019) = \cite{bnf2019online}

British National Formulary [Online], 2019. London: Pharmaceutical Press. Available from: \url{https://www.medicinescomplete.com/#/browse/bnf} [Accessed 26 November 2019].


(\emph{Aspirin}, 2021) = \cite{aspirin2021bnf}

\emph{Aspirin} [Online], 2021. London: Pharmaceutical Press. Available from: \url{https://www.medicinescomplete.com/#/content/bnf/_456850132} [Accessed 26 November 2021].


RX: (British National Formulary, 2020) = \cite{aspirin2020bnf}

British National Formulary, 2020. 79th ed. \emph{Aspirin}. London: Pharmaceutical Press.


RX: (British National Formulary, 2019) = \cite{aspirin2019bnf}

British National Formulary, 2019. \emph{Aspirin} [Online]. London: Pharmaceutical Press. Available from: \url{https://www.medicinescomplete.com/#/content/bnf/_456850132} [Accessed 26 November 2019].



\subsubsection*{Chapter\slash paper from a collection (by different authors) in an edited book}

RL: (Burchard, 1965) = \cite{burchard1965hhl}

Burchard, J.E., 1965. How humanists use a library. In: C.F.J. Overhage and J.R. Harman, eds. \emph{Intrex: report on a planning conference and information transfer experiments}. Cambridge, Mass.: MIT Press, pp.41--87.


RX: (Reid, 1967) = \cite{reid1967ptp}

Reid, D.R., 1967. Physical testing of polymer films. In: S.H. Pinner, ed. \emph{Modern packaging films}. London: Butterworths, pp.143--183.



\subsection{Articles and periodicals}

\subsubsection*{Journal article}

RL: (Stieg, 1981a) = \cite{stieg1981cer}

Stieg, M.F., 1981a. Continuing education and the reference librarian in the academic and research library. \emph{Library journal}, 105(22), pp.2547--2551.

RL: (Stieg, 1981b) = \cite{stieg1981inh}

Stieg, M.F., 1981b. The information needs of historians. \emph{College and research libraries}, 42(6), pp.549--560.


RX: (Newman, 2010) = \cite{newman2010mcb}

Newman, R., 2010. Malaria control beyond 2010. \emph{Brit. Med. J.}, 341(7765), pp.157--208.


RX: (Wetzstein et al., 2020) = \cite{wetzstein.etal2020iai}

Wetzstein, G., Ozcan, A., Gigan, S., Fan, S., Englund, D., Soljacic, M., Denz, C., Miller, D.A.B. and Psaltis, D., 2020. Inference in artificial intelligence with deep optics and photonics. \emph{Nature}, 588(7836), pp.39--47.



\subsubsection*{Electronic journal article}

RX: (Devlin, Martin and Ostrovnaya, 2021) = \cite{devlin.etal2021ipp}

Devlin, S.M., Martin, A. and Ostrovnaya, I., 2021. Identifying prognostic pairwise relationships among bacterial species in microbiome studies. \emph{PLOS Computational Biology} [Online], 17(11). Available from: \url{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1009501} [Accessed 9 December 2021].


RX: (Steward, Connelly and Robinson, 2020) = \cite{steward.etal2020eys}

Steward, S., Connelly, D. and Robinson, J., 2020. Everything you should know about the coronavirus outbreak. \emph{The pharmaceutical journal} [Online]. Available from: \url{https://www.pharmaceutical-journal.com/news-and-analysis/features/everything-you-should-know-about-the-coronavirus-outbreak/20207629.article} [Accessed 30 April 2020].



\subsubsection*{Pre-publication e-journal article}

Give `in press' or `preprint' as the \texttt{volume} number.

RX: (Liontou et al., 2019) = \cite{liontou.etal2019dra}

Liontou, C., Kontopodis, E., Oikonomidis, N., Maniotis, C., Tassopoulos, A., Tsiafoutis, I., Lazaris, E. and Koutouzis, M., 2019. Distal radial access: a review article. \emph{Cardiovascular revascularization medicine} [Online], in press. Available from: \url{https://www.sciencedirect.com/science/article/pii/S1553838919303367} [Accessed 19 June 2019].



\subsubsection*{Preprint or trial study in a digital repository}

Record these as \texttt{report}s, with the name of the digital repository as the \texttt{archive}.

RX: (Shah and Corrick, 2016) = \cite{shah.corrick2016hsc}

Shah, I. and Corrick, I., 2016. \emph{How should central banks respond to non-neutral inflation expectations?} Bath: University of Bath. \emph{OPUS} [Online]. Available from: \url{http://opus.bath.ac.uk} [Accessed 4 May 2016].


RX: (Ganju, 2021) = \cite{ganju2021sed}

Ganju, V., 2021. \emph{A study of EnGeneIC Dream Vectors (EDV's) packaged with the chemotherapy, E-EDV-D682 given simultaneously as non-targeted EDVs carrying an immune enhancer called EDV-GC, in participants with advanced pancreatic and other cancers whose disease has progressed after one or two treatment regimes, or where other standard therapies are not appropriate}. Sydney: University of Sydney. \emph{Australian and New Zealand Clinical Trials Registry} [Online]. Available from: \url{http://www.anzctr.org.au/Trial/Registration/TrialReview.aspx?id=365258} [Accessed 29 April 2021].



\subsubsection*{Newspaper article}

Record these as \texttt{article-newspaper}. There is also \texttt{article-magazine} for magazine articles.

RX: (Haurant, 2004) = \cite{haurant2004bbh}

Haurant, S., 2004. Britain's borrowing hits £1 trillion. \emph{The Guardian}, 29 July, p.16c.


RX: (The Independent, 1992) = \cite{independent1992pub}

The Independent, 1992. Picking up the bills. \emph{The Independent}, 4 June, p.28a.


RX: (Cogley, 2020) = \cite{cogley2020ccs}

Cogley, M., 2020. Corporate confidence slumps to record low. \emph{The Telegraph} [Online], 4 May. Available from: \url{https://www.telegraph.co.uk/business/2020/05/03/corporate-confidence-slumps-all-time-low/} [Accessed 5 May 2020].



\subsection{Conference papers}

\subsubsection*{Conference paper (when proceedings have a named editor)}

RX: (Crawford, 1965) = \cite{crawford1965oim}

Crawford, G.I., 1965. Oxygen in metals. In: J.M.A. Lenihan and S.J. Thompson, eds. \emph{Activation analysis: proceedings of a NATO Advanced Study Institute}, 2--4 August 1964, Glasgow. London: Academic Press, pp.113--118.



\subsubsection*{Conference paper (when proceedings have no named editor or are part of a major series)}

RX: (Soper, 1972) = \cite{soper1972rbc}

Soper, D., 1972. Review of bracken control experiments with asulam. \emph{Proceedings of the 11th British Weed Control Conference}, 15--17 November 1972, Brighton. Brighton: University of Sussex, pp.24--31.



\subsection{Grey literature}

\subsubsection*{Thesis/dissertation}

RX: (Burrell, 1973) = \cite{burrell1973ist}

Burrell, J.G., 1973. \emph{The importance of school tours in education}. Thesis (M.A.). Queen's University, Belfast.



\subsubsection*{Report, working paper, or research briefing}

RX: (UNESCO, 1993) = \cite{unesco1993gip}

UNESCO, 1993. \emph{General information programme and UNISIST}. (PGI-93/WS/22). Paris: UNESCO.


RX: (BRE, 2007) = \cite{bre2007dqb}

BRE, 2007. \emph{Designing quality buildings: a BRE guide}. (Report 497). Bracknell: BRE.


RX: (Deneulin and Dinerstein, 2010) = \cite{deneulin.dinerstein2010hms}

Deneulin, S. and Dinerstein, A.C., 2010. \emph{Hope movements: social movements in the pursuit of human development}. (Bath papers in international development and wellbeing, no.~8). Bath: University of Bath.



\subsubsection*{Standard}

RX: (BSI, 1990) = \cite{bs5605:1990}

BSI, 1990. \emph{BS~5605:1990 Recommendations for citing and referencing published material}. London: BSI.


RX: (ASTM, 2019) = \cite{astm.d1655}

ASTM, 2019. \emph{ASTM D1655 - 19 Standard specification for aviation turbine fuels}. West Conshohocken, Pa.: ASTM.



\subsubsection*{Patent}

RX: (Phillipp Morris Inc., 1981) = \cite{pm1981opa}

Phillipp Morris Inc., 1981. \emph{Optical perforating apparatus and system}. European patent application 0021165A1. 1981-01-07.



\subsubsection*{Unpublished written material and personal communications}

Put `Unpublished' in the \texttt{annote} field.

RX: (Harris, 2013) = \cite{harris2013fgr}

Harris, G., 2013. \emph{Focus group recommendations: internal task group report}. Unpublished.


RX: (Hadley, 2015) = \cite{hadley2015bir}

Hadley, S., 2015. \emph{Biomechanics: introductory reading, BM289: sport biomechanics}. University of Bath. Unpublished.


RX: (Thomas, 2015) = \cite{thomas2015wcr}

Thomas, D., 2015. Word count and referencing style. \emph{Frequently asked questions discussion board: PHYS 2011: housing studies}. University of Bath. Unpublished.



\subsection{Audiovisual materials}

\subsubsection*{Image}

RI: (NASA, 2015) = \cite{nasa2015nat}

NASA, 2015. \emph{NASA astronaut Tim Kopra on Dec. 21 spacewalk} [Online]. Washington: NASA. Available from: \url{http://www.nasa.gov/image-feature/nasa-astronaut-tim-kopra-on-dec-21-spacewalk} [Accessed 7 January 2015].


RI: (Iliff, 2006) = \cite{iliff2006rcb}

Iliff, D., 2006. \emph{Royal Crescent in Bath, England - July 2006} [Online]. San Francisco: Wikimedia Foundation. Available from: \url{https://commons.wikimedia.org/wiki/File:Royal_Crescent_in_Bath,_England_-_July_2006.jpg} [Accessed 7 January 2016].


RI: (Bristol Region Building Record, 1965) = \cite{brbr1965gph}

Bristol Region Building Record, 1965. \emph{Green Park House (since demolished), viewed from southwest} [Photograph]. BRBR, D/877/1. Archives \& Research Collections, University of Bath Library.



\subsubsection*{Map}

RX: (Andrews and Dury, 1773) = \cite{andrews.dury1773wilts}

Andrews, J. and Dury, A., 1773. \emph{Map of Wiltshire}, 1 inch to 2 miles. Devizes: Wiltshire Record Society.


RX: (Ordnance Survey, 2020) = \cite{os2020bath}

Ordnance Survey, 2020. \emph{Street view map of University of Bath} [Online], 1:5000, OS VectorMap® Local. Available from: \url{https://digimap.edina.ac.uk/roam/map/os} [Accessed 30 April 2020].


RX: (Google, 2020) = \cite{google2020harbourside}

Google, 2020. \emph{Harbourside, Bristol} [Online], Google Maps. Available from: \url{https://www.google.co.uk/maps/place/Harbourside,+Bristol/} [Accessed 30 April 2020].



\subsubsection*{Film, video or DVD}

RX: (\emph{Macbeth}, 1948) = \cite{macbeth1948}

\emph{Macbeth}, 1948. Film. Directed by Orson Welles. USA: Republic Pictures.


RX: (\emph{The elephant man}, 1980) = \cite{elephant-man1980}

\emph{The elephant man} [Online], 1980. Film. Directed by David Lynch. USA: Brooksfilms. Available from: BBC iPlayer [Accessed 4 May 2021].



\subsubsection*{Online video\slash audio}

RX: (Moran, 2016) = \cite{moran2016sol}

Moran, C., 2016. \emph{Save our libraries} [Online]. Available from: \url{https://www.youtube.com/watch?v=gKTfCz4JtVE&feature=youtu.be} [Accessed 29 April 2016].


RX: (Chakrabarti, 2016) = \cite{chakrabarti2016hac}

Chakrabarti, V., 2016. \emph{How architecture and city planning can combat social inequality} [Online]. Available from: \url{https://www.curbed.com/2016/5/5/11593058/vishaan-chakrabarti-pau-curbed-appeal-podcast} [Accessed 28 March 2019].



\subsubsection*{Television or radio broadcast}

RX: (Hurry up and wait, 2021) = \cite{inn2021huw}

Hurry up and wait, 2021. \emph{Inside no.9}, \emph{Episode 6:4}. TV. BBC2, 31 May. 21.30 hrs.


RX: (Rick Stein’s French odyssey, 2006) = \cite{rsfo2006ep5}

Rick Stein's French odyssey: Episode 5, 2006. TV. BBC2, 23 August. 20.30 hrs.


RX: (The Archers, 2006) = \cite{archers20060823}

The Archers, 2006. Radio. BBC Radio 4, 23 August. 19.02 hrs.


RX: (The secret, 2020) = \cite{tkmmm2020ts}

The secret, 2020. \emph{Tiger king: murder, mayhem and madness}, \emph{Episode 3} [Online]. TV. Available from: Netflix [Accessed 4 May 2021].



\subsubsection*{Music score}

RX: (Beethoven, 1950) = \cite{beethoven1950symph1}

Beethoven, L. van, 1950. \emph{Symphony no.1 in C, Op.21}. Harmondsworth: Penguin.



\subsection{Digital media}

\subsubsection*{Website or webpage}

RX: (World Health Organization, 2018) = \cite{who2018ttc}

World Health Organization, 2018. \emph{The top 10 causes of death} [Online]. Geneva: World Health Organization. Available from: \url{https://www.who.int/news-room/fact-sheets/detail/the-top-10-causes-of-death} [Accessed 29 June 2020].


RX: (Manco, 2013) = \cite{manco2013va}

Manco, J., 2013. \emph{Vernacular architecture} [Online]. Available from: \url{https://www.buildinghistory.org/style/vernacular.shtml} [Accessed 20 February 2020].



\subsubsection*{Social media}

RX: (Gaiman, 2021) = \cite{gaiman2021fbp}

Gaiman, N., 2021. \emph{Facebook post} [Online], 21 April. Available from: \url{https://www.facebook.com/neilgaiman/posts/305187897642814} [Accessed 13 May 2021].


RX: (Library at University of Bath, 2021) = \cite{ublib2021tp}

Library at University of Bath [@bathunilibrary], 2021. \emph{Twitter post} [Online], 10 May. Available from: \url{https://twitter.com/BathUniLibrary/status/1391774402618998795?s=20} [Accessed 12 May 2021].


RX: (University of Bath Library, 2021) = \cite{ublib2021ip}

University of Bath Library [@unibathlib], 2021. \emph{Instagram post} [Online], 15 March. Available from: \url{https://www.instagram.com/p/CMb5GHjFv9A/?utm_source=ig_web_copy_link} [Accessed 7 May 2021].



\subsubsection*{Email discussion lists (jiscmail\slash listserv etc.)}

RX: (Clark, 2004) = \cite{clark2004euk}

Clark, T., 5 July 2004. A European UK Libraries Plus? \emph{Lis-link} [Online]. Available from: \url{lis-link@jiscmail.ac.uk} [Accessed 30 July 2004].



\subsubsection*{Database}

RX: (Bureau van Dijk, 2008) = \cite{bvd2008bt}

Bureau van Dijk, 2008. \emph{BT Group plc company report}. \emph{FAME} [Online]. London: Bureau van Dijk. Available from: \url{http://www.portal.euromonitor.com} [Accessed 6 November 2014].



\subsubsection*{Dataset}

RX: (Wilson, 2013) = \cite{wilson2013rgc}

Wilson, D., 2013. \emph{Real geometry and connectedness via triangular description: CAD example bank} [Online]. Bath: University of Bath. Available from: \url{https://doi.org/10.15125/BATH-00069} [Accessed 20 April 2016].



\subsubsection*{Computer program}

RX: (@screencasto, n.d.) = \cite{screencasto}

@screencasto, n.d. \emph{Screencast-O-Matic} (v.2) [computer program]. Available from: \url{https://screencast-o-matic.com/} [Accessed 16 May 2016].



\subsection{Works in languages other than English}

Put the translated title in \texttt{original-title}, even though it isn't.

\subsubsection*{Work in translation}

RX: (Aristotle, 2007) = \cite{aristotle2007ne}

Aristotle, 2007. \emph{Nicomachean ethics} (W.D. Ross, Trans.). South Dakota: NuVisions.



\subsubsection*{Work in the Roman alphabet}

RX: (Esquivel, 2003) = \cite{esquivel2003cap}

Esquivel, L., 2003. \emph{Como agua para chocolate} [Like water for chocolate]. Barcelona: Debolsillo.



RX: (Thurfjell, 1975) = \cite{thurfjell1975vhv}

Thurfjell, W., 1975. Vart har våran doktor tagit vägen? [Where has our doctor gone?]. \emph{Läkartidningen}, 72, p.789.



\subsubsection*{Work in a non-Roman alphabet}

RX: (Hua, 1999) = \cite{hua1999qys1}

Hua, L. 華林甫, 1999. Qingdai yilai Sanxia diqu shuihan zaihai de chubu yanjiu 清代以來三峽地區水旱災害的初步硏 [A preliminary study of floods and droughts in the Three Gorges region since the Qing dynasty]. \emph{Zhongguo shehui kexue \emph{中國社會科學}}, 1, pp.168--79.


RX: (Hua, 1999) = \cite{hua1999qys2}

Hua, L., 1999. Qingdai yilai Sanxia diqu shuihan zaihai de chubu yanjiu [A preliminary study of floods and droughts in the Three Gorges region since the Qing dynasty]. \emph{Zhongguo shehui kexue}, 1, pp.168--79.


RX: (Pamporov, 2006) = \cite{pamporov2006rvb}

Pamporov, A., 2006. \emph{Romskoto vsekidnevie v Balgariya} [Roma everyday life in Bulgaria]. Veliko Tarnovo: Faber.



\subsection{Legal or government document: UK parliamentary reports\slash legislation}

% Parliamentary reports

\subsubsection*{House of Commons paper}

RX: (Great Britain. Parliament. House of Commons, 2004) = \cite{gb.hc2003/04-30}

Great Britain. Parliament. House of Commons, 2004. \emph{National Savings investment deposits: account 2002--2003}. (HC 2003/04, 30). London: National Audit Office.



\subsubsection*{House of Lords paper}

RX: (Great Britain. Parliament. House of Lords, 1987) = \cite{gb.hl1986/87-66}

Great Britain. Parliament. House of Lords, 1987. \emph{Social fund (maternity and funeral expenses) bill}. (HL 1986/87, (66)). London: HMSO.



\subsubsection*{Command paper}

RX: (Great Britain. Ministry of Defence, 2004) = \cite{gb.cm6041}

Great Britain. Ministry of Defence, 2004. \emph{Delivering security in a changing world: defence white paper}. (Cm. 6041). London: TSO.



% UK Primary Legislation

\subsubsection*{House of Commons\slash House of Lords bill}

RX: (Great Britain. Parliament. House of Commons, 1988) = \cite{gb.bill1987/88-66}

Great Britain. Parliament. House of Commons, 1988. \emph{Local government finance bill}. (Bills | 1987/88, 66). London: HMSO.



\subsubsection*{Act of Parliament (UK Statutes) before 1963}

RX: (\emph{Witchcraft Act}, 1735) = \cite{gb.wa1735}

\emph{Witchcraft Act} \emph{1735} (9 Geo.2, c.5).



\subsubsection*{Act of Parliament (UK Statutes) 1963 onwards}

RX: (\emph{Pensions Act}, 2014) = \cite{gb.pa2014}

\emph{Pensions Act} \emph{2014}, c.19. London: TSO.



% UK secondary legislation

\subsubsection*{Statutory instrument}

RX: (\emph{The Human Medicines Regulations}, 2012) = \cite{gb.hmr2012}

\emph{The Human Medicines Regulations} \emph{2012} [Online], No.1916, United Kingdom: HMSO. Available from: \url{http://www.legislation.gov.uk/uksi/2012/1916/pdfs/uksi_20121916_en.pdf} [Accessed 17 April 2016].



\subsection{Legal or government document: EU reports\slash legislation}

% European reports

\subsubsection*{EU publication}

RX: (European Commission, 2015) = \cite{ec2015gra}

European Commission, 2015. \emph{General report on the activities of the European Union 2014}. Luxembourg: Publications Office of the European Union.



% European legislation

\subsubsection*{EU regulation or directive, decision, recommendation or opinion}

RX: (Council Regulation (EC) 1984/2003, 2003) = \cite{eu.dir1984/2003}

Council Regulation (EC) 1984/2003 of 8 April 2003 introducing a system for the statistical monitoring of trade in bluefin tuna, swordfish and big eye tuna within the Community [2003] \emph{OJ} L295.



\subsection{Legal or government document: case reports}

\subsubsection*{Legal case study}

RX: (\emph{Seldon v.~Clarkson Wright \& Jakes}, 2012) = \cite{seldon-v-c.w.j2012}

\emph{Seldon v.~Clarkson Wright \& Jakes}. [2012]. UKSC 16.



\subsubsection*{Judgment of the European Court of Justice}

RX: (\emph{Alessandrini Srl and others v.~Commission}, 2005) = \cite{srl.etal-v-comm2005}

\emph{Alessandrini Srl and others v.~Commission} (C-295/03 P) [2005] ECR I--5700.


